% moderncv themes
% style options are 'casual' (default), 'classic', 'banking', 'oldstyle' and 'fancy'
\moderncvstyle{classic}                             
% color options 'black', 'blue' (default), 'burgundy', 'green', 'grey', 'orange', 'purple' and 'red'
\moderncvcolor{burgundy}                               
\usepackage{libertine}

% Social icons
\social[linkedin][www.linkedin.com/in/david-k-6a57771a1/]{David Kleingeld}
\social[github]{dvdsk}
\homepage{davidsk.dev}

\def\texthl#1{\textbf{#1}}

\usepackage{tikz}
\newcommand{\ExternalLink}{%
    \tikz[x=1.2ex, y=1.2ex, baseline=-0.05ex]{% 
        \begin{scope}[x=1ex, y=1ex]
            \clip (-0.1,-0.1) 
                --++ (-0, 1.2) 
                --++ (0.6, 0) 
                --++ (0, -0.6) 
                --++ (0.6, 0) 
                --++ (0, -1);
            \path[draw, 
                line width = 0.5, 
                rounded corners=0.5] 
                (0,0) rectangle (1,1);
        \end{scope}
        \path[draw, line width = 0.5] (0.5, 0.5) 
            -- (1, 1);
        \path[draw, line width = 0.5] (0.6, 1) 
            -- (1, 1) -- (1, 0.6);
        }
    }

\definecolor{compl_burgundy}{rgb}{0, 0.40, 0.40}
\newcommand\myhref[3][compl_burgundy]{\href{#2}{\color{#1}#3\,\ExternalLink}}

\raggedright

\begin{document}
\makecvtitle

\section{Summary}
I am a software engineer experienced in building async services. I work with a focus on maintainability. I have deployed to Linux hosts and have worked with tools like Docker, SystemD and HaProxy. My open source projects include a distributed file system and a macro to turn a struct into a typed database. Serving as chair of the Faculty Council, I have led meetings and helped shape University policy. I enjoy teaching my programming group to write beautiful code.

\section{Education}
\cventry{2019--2022}{MSc Computer Science}{Leiden University}{}{\texthl{Cum Laude}}{Focused on cloud and distributed computing, explored other fields including AI, robotics and CS-theory \\ \textit{Thesis: \myhref{https://davidsk.dev/thesis}{GovFs}, a highly scalable consistent distributed file system}} % TODO add thesis title keep if relevant
\cventry{2014--2019}{Double BSc Physics and Astronomy}{Leiden University}{}{}{}

\section{Skills}
\subsection{Software Engineering}
While developing I aim to build readable code that is easy to change. I can then more easily turn into high performance code where needed. I have adopted \texthl{test driven development} as it makes refactoring less risky, meaning it is much easier (and realistic) to maintain a clean and readable code-base. Building a \texthl{distributed} file system I experienced the importance of running test under high load. To keep my software engineering skills growing I engage with large open source projects, read great titles such as "The Pragmatic Programmer" and "Refactoring", and explore these ideas in side projects.

\subsection{Programming Languages}
\begin{itemize}
	\item \textbf{Rust}: I love writing Rust code. I believe it has made me a better programmer, I have become more aware of object and reference \texthl{lifetimes} and how to use \texthl{concurrency} safely when using other languages. 
	\item \textbf{C++}: has major issues regarding memory safety. I try to mitigate this by using the standard library in debug mode, using \texthl{address sanitizer} and encapsulating resources where possible. 
	\item \textbf{Python}: I am a strong proponent of type hinting in Python as it helps linters detect more errors before run-time. I use Python for a wide variety of tasks ranging from data science to building \texthl{scaling cloud} systems.
	\item \textbf{Bash/Unix CLI}: Because of there ubiquity I have become quite proficient at using Bash and CLI tools to automate \texthl{DevOps} tasks, such as: deployment, monitoring a cluster and filtering megabytes of logs. I would not, however, use the error-prone arcane wizardry of Bash outside of development and testing.
	\item \textbf{Lua}: I have used Lua to script a large \texthl{Neovim} plugin. I appreciate its performance, though found it is a challenge to structure code well.
\end{itemize}


\subsection{DevOps}
\begin{itemize}
	\item \textbf{Linux}: I have used Linux on my desktop and servers since 2014. After trying Fedora and Debian, I settled on using Pop!\_OS as my daily driver, because it offers stability and LTS as well as up-to-date packages. 	
	\item \textbf{Sandboxing}: My services are sandboxed with \textbf{SystemD} instead of container engines such as \textbf{Docker} and \textbf{Podman}. I use these to simplify setting up reproducible builds and run-time environments.
	\item \textbf{Architecture}: I use a \textbf{micro-services} architecture for some of my larger projects. I use \textbf{HaProxy} for both HTTP and TCP TLS termination and routing.
\end{itemize}

\section{Experience}
\subsection{Open Source}
\cvitemwithcomment{\myhref{https://crates.io/crates/instance-chart}{Instance-chart}}{Rust}{A typed alternative to mDNS, for service discovery on the same network or machine.}
\cvitemwithcomment{\myhref{https://github.com/dvdsk/dbstruct}{dbstruct}}{Rust}{A macro to turn a struct into a typed database}
\cvitemwithcomment{\myhref{https://github.com/dvdsk/WorldSync}{WorldSync}}{Rust}{A GUI client and server binary to host a Minecraft Server on demand on users' machines and synchronize the world}
\cvitemwithcomment{\myhref{https://github.com/dvdsk/dataserver}{Dataserver}}{Rust}{A compact time series data backend optimized for linear searches}

Other projects include: cross-platform \myhref{https://github.com/dvdsk/pods}{podcast player} and \myhref{https://github.com/dvdsk/alarm}{alarm} apps, a \myhref{https://github.com/dvdsk/HomeAutomation}{home automation system} which has been in use, expanded and \texthl{maintained} for over 5 years. Furthermore, I dabble in \textbf{async embedded} building a basic \myhref{https://github.com/dvdsk/rustyscopes}{oscilloscope}. Finally, I worked on a Neovim extension for grammar, spelling and style checker in strings and comments.\\
\smallskip
I have contributed code to various projects on \texthl{GitHub} and recently contributed a \myhref{https://github.com/rust-lang/libs-team/issues/55}{proposal} for expanding the \texthl{Rust} standard library.

\subsection{Other}
I served one year as \textbf{Chair of the Faculty Council} leading the council meetings and successfully negotiating to keep a number of courses available to all students.
I really value my years of giving demonstrations and \textbf{tours to the public} at the old observatory in Leiden and \textbf{training} groups of aspirant tour guides.\\
\smallskip
Recently I have started a small programming study group where I \textbf{teach} Rust and modern extendible Python to computer science students.

\end{document}
